\label{chapter:introduction}

The trend of home automation is on the rise in today's world. From energy-saving applications to fancy lighting controls, home automation has become a global phenomenon. It's human nature to look for the easiest solution. This attitude promotes innovation and productivity \cite{hassan_2018}. Mail is part of the postal system that delivers written documents in the form of envelopes and small parcels to recipients all over the world. In the late 1990s, e-mail dominated the mailing system since it was faster and cheaper than the postal service and enabled users to communicate worldwide. Nonetheless, most of our vital documents and official documents are sent in the conventional manner which is our postal system \cite{Subramaniam2007}.

The existence of electronic mail (e-mail) has caused most people to forget to check their physical post-box. Additionally, because of their busy lives, people do not have time to check their post-box regularly. Oftentimes, these situations have led to the loss of important notices or mails and even cause them to become insensitive to the presence of such notices in the first place \cite{Muhamaad_2019}.

Smart Post-box has found a new revolution in using newer technologies to alert the users on the event a mail is delivered, especially through e-mail.

\section{Objectives}
This project was implemented based on a review of current mail boxing approaches.
Users frequently lose and leave mail sent and placed in mailboxes. The major objective of this project is to notify the owner of the post-box. Specific objectives are: 

\begin{itemize}
  \item To collect the data from the ultrasonic sensor and send it to the micro-controller unit, which is NodeMCU.
  \item To update the data in the Firebase.
  \item To trigger an event based on distance.
  \item Finally, the owner should be notified by sending an email if the measured distance is less than 8.
\end{itemize}