\label{chapter: State of Art}

In this section, we've looked at some of the previous trials and detailed some of the methodologies and operational ideas that were employed.

Supraja C D and Bindusree V created namely making bell notifications which are used to help deaf people to respond to bell sounds. In this study, the message will be sent via a wireless module, with one module installed on the doorbell, and the other module will be connected to the user, with several LED/vibration motors installed as an indication so that the LCD screen will display text for notification purposes. The Arduino Control Unit controls these modules \cite{devi2019}.

Lidzatus S created a doorbell whose purpose is to help solve some of the problems that occur in everyday life, especially for hosts who don't hear the sound of the bell because they have problems hearing or don't hear the sound of the bell because they are playing a gadget complete with earphones, this system is designed by using the wifi module Node-MCU ESP8266 as a control to send notifications to e-mail \cite{setiawan2021}.

Bindu Sebastian, Mashitha, and Meghana created a project named an intelligent mailbox system that is capable of automatically sending information about mail to users and delivering notifications to courier officials using GSM and RFID technology. They have used a dc motor for opening and closing a mailbox, so it can provide security to the system \cite{Sebastian2016}.

The Smart system letterbox was developed by Anjali Devi Pujari, Priyanka Bansode, Pragati Girme, Harshal Mohite, and Anirudha Pande, in which a hardware kit alerts the user that a letter has arrived. Notifications are received through the mobile application. The obstacle sensor is used to identify objects (letters). Using the RTC clock, the delivery time of the letter can be stored. Through the GSM module, the notification is sent by message and the GPS module detects the location at which the letter has been received \cite{Bansode2016}.

Siva Kumar Subramaniam, Siti Huzaimah Binti Husin, Yusmarnita Binti Yusop, Abdul Hamid bin Hamidon created a Real-time mailbox alert system via SMS or email in that this system, Mails delivered into the user’s mailbox, the system will automatically generate an alert which is sent in the form of a short message system or email that typically details the real-time of mail delivery. The system is designed to ease human life by sending SMS or email to notify the user about important new mails reaching the user’s mailbox \cite{Subramaniam2007}.
